Appendix

### 2021-03-13 appendix.Rmd
Update renv

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

# Reproducing the results for other cities

To reproduce the results presented for Manchester for other cities there are a few computing pre-requisites:

- A reasonably powerful computer, e.g. with 8 GB RAM
- The statistical programming language R installed (we recommend running it in the RStudio editor)
- The source code of the paper repository, which can be download from `url TBC`

```{r, eval=FALSE, echo=FALSE}
required_packages = renv::dependencies()
renv::snapshot()
```

# Birmingham

# Leeds

# Nottingham
